Draft Research pt2

### 2019-03-10 draftResearch_pt2.Rmd
Trying some adjustments to pitching z-scores for comparison to batters

# Generate rankings
```{r}
z_score_count <- function(df, stat, invert=FALSE) {
  stat <- enquo(stat)
  col_nm <- paste0("z_", quo_name(stat))

@@

@@

z_score_rate <- function(df, stat, quantity, invert=FALSE) {
  stat <- enquo(stat)
  quantity <- enquo(quantity)
  col_nm <- paste0("z_",quo_name(stat))

@@

##### QS
```{r}

### To Do
1. Strategy for projecting scoring stats not in this data set (i.e. CG/SHO, etc)
2. Validate findings, control z-scores between batters and players to make them comparable
3. visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
4. Develop tiers of players (linear model? nearest neighbor?)
5. Replacement level stuff (new section)

>>>>

# Generate rankings
```{r}
z_score_count <- function(df, stat, invert=FALSE, multiplier=1) {
  stat <- enquo(stat)
  col_nm <- paste0("z_", quo_name(stat))

@@

  if (multiplier != 1) {
    df %>%
      mutate(s_z = multiplier * s_z) -> df
  }

@@

z_score_rate <- function(df, stat, quantity, invert=FALSE, multiplier = 1) {
  stat <- enquo(stat)
  quantity <- enquo(quantity)
  col_nm <- paste0("z_",quo_name(stat))

@@

##### QS
Struggling to find meaningful QS data to work with, but again, I'm thinking the takeaway will be more weighting on ERA & WHIP.

##### Z-Score Adjustments
I originally added a multiplier of 3 to two of the pitching categories, so that it would mean there were "nine" categories for both pitching and batting that make up the z_sum. 
The result was that pitching z_sums had a much wider range, to the point where three pitchers had a higher z_sum than Mike Trout, who was coming out roughly as valuable as Justin Verlander. 
Weighting the categories so that there would be an "equal" number of categories felt right, but I wonder if that's giving too much credit to scarce categories like CG/SHO. 
For now, I've set the multiplier to 2. The results are still a bit "scandalous" (Mookie Betts going after Sale/deGrom/Scherzer) but this is a better starting point for a conversation.
Need to take a deeper look into how I'm comparing the relative value between pitcher and catcher rather than setting the multiplier to get results I'm expecting. 
```{r}
(z_pitchers_adj <- pitchers %>%
  filter(ADP < 999) %>%
  z_score_count(SV) %>%
  z_score_count(HLD) %>%
  z_score_rate(ERA, IP, TRUE, multiplier=2) %>%
  z_score_count(SO) %>%
  z_score_rate(WHIP, IP, TRUE, multiplier=2) %>%
  mutate(
    z_sum = pmap_dbl(
      select(., starts_with("z_")), 
      sum
    )
  ) %>%
  arrange(desc(z_sum))
)

(z_compare_adj <- z_batters %>% 
  mutate(type = "Batter") %>%
  bind_rows(z_pitchers_adj) %>%
  mutate(type = if_else(is.na(type), "Pitcher", type)) %>%
  arrange(z_sum %>% desc()) %>%
  mutate(ovrl_rank = row_number()))

z_compare_adj %>% saveRDS("data/z_compare_adj.Rds")

z_compare_adj %>%  
  filter(Name == "Miguel Cabrera" | Name == "Kyle Freeland") %>% 
  View()

z_compare_adj %>%
  ggplot(aes(x=ADP,y=z_sum,color=type)) +
  geom_point(aes(text=Name)) -> p_adj

plotly::ggplotly(p_adj)
```

### To Do
1. Validate findings, control z-scores between batters and players to make them comparable
2. visualize - adjust plotly hover over detail to include player name (or maybe just playerid?)
3. Develop tiers of players (linear model? nearest neighbor?)
4. Replacement level stuff (new section)
